Efficient Handling of String-Number Conversion

### 2019-11-21 draft.tex

The semantics of a string constraint $\phi$ restricted by $\dr$ is then defined as 
$\semof{\phi}^\dr = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{\dr(x)}\} \subseteq \vars\times \varn \rightarrow \Sigma^* \times\nat$.
The following sections will be devoted to describing the flattening of the atomic string constraints. 
The correctness of the entire construction of $\outlf$ is expressed by  Theorem~\ref{theorem:correct}:
\begin{theorem}\label{theorem:correct}
$\decode \dr (\semof {\outlf}) = \semof{\insc}^\dr$ 
\end{theorem}

>>>>

The semantics of a string constraint $\phi$ restricted by $\dr$ is then defined as 
$\semof{\phi}^\dr = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{\dr(x)}\} \subseteq \vars\times \varn \rightarrow \Sigma^* \times\nat$.
The following sections will be devoted to describing the flattening of the atomic string constraints.

The correctness of the entire construction of $\outlf$ is expressed by  Theorem~\ref{theorem:correct}. 
It uses the decoding function $\decode \dr$ parameterised by the domain restriction $\dr$. 
For an interpretation $e \cup I'$ consisting of an interpretaton $e$ of $V_\dr$ and $\#V_\dr$ and an interpretation fo integer variavles $I'$, we let $\decode \dr (e\cup I') = (I \cup I')$ where $I$ is the interpretation of string variables such that for each $x\in X$,
$I(x) = \decode {\dr(x)} (e_{V_{\dr(x)}\cup \#V_{\dr(x)}})$. That is, $\decode \dr (e\cup I')$ returns the original integer interpretation $I'$ together with each string variable $x$ interpreted as the $\decode {\dr(x)}$-decoding of the values of $V_{\dr(x)}$ and $\#V_{\dr(x)}$. 
We lift $\decode \dr$ to sets of interpretations in the standard manner.
\begin{theorem}\label{theorem:correct}
$\decode \dr (\semof {\outlf}) = \semof{\insc}^\dr$ 
\end{theorem}
